Capstone Movielens Report

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Refactoring (in progress): K-Fold Cross-Validation citing.

In our project this function is used to clamp the computed movie rating values between 0.5 and 5.
:::

@@

Calculates the average value of the *Mean Squared Errors* calculated using the *K-Fold Cross-Validation* method as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].

@@

::: { #func.mse_cv.args.r_list .sidebar }
  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF], calculated in `K`th iteration using the *K-Fold Cross-Validation* method.

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom function [put_log2](#func.put_log2) described above in the [Logging Functions] section of *This Appendix*.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom function [put_log1](#func.put_log1) described above in the [Logging Functions] section of *This Appendix*.
:::
:::

@@

Aggregates the input data frames into a single data frame.

@@

::: { #func.union_cv_results.args.data_list .sidebar }
  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* method execution.

::: { #func.union_cv_results.details .sidebar }
##### Details
\
This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame for further processing.
:::

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in our project we use `K = 5`).

@@

The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in our project we use `K = 5`).

@@

The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::

@@

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
:::
:::

@@

Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::
:::

@@

The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::
:::

@@

The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.

@@

Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
:::
:::

@@

::: { #func.train_user_movie_genre_effect.details .sidebar }
##### Details
\
The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *This Appendix*.

@@

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
:::
:::

@@

Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
:::
:::

@@

The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::

@@

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
:::
:::

@@

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function (described below in section [UMGYE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.train_UMGY_effect.cv.usage) subsection of *This Function's Description Section* below.
:::

@@

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
:::
:::

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function described below in section [UMGYE Model: Regularization] of *This Appendix*.
:::

@@

The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

@@

Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
:::
:::

@@

This is a helper function that computes the *Day General Effect(hereafter DG Effect or DGI for short)* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#func.calc_day_general_effect.args.train_set) argument, and is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).

@@

The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::

@@

This is a helper function that calculates the *Day General Effect* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _5-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.

::: { #func.calc_day_general_effect.cv.usage .sidebar }
##### Usage
\
```{r eval=FALSE}
calc_day_general_effect.cv(lambda) |> calc_UMGY_effect()  
```

@@

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

Below is a simplified version of the source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) function:
```{r eval=FALSE}
calc_day_general_effect.cv <- function(lambda = 0){

  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
    cv_fold_dat$train_set |> calc_day_general_effect(lambda)
  })
  put_log1("Function `calc_day_general_effect.cv`:
Date Global Effect list has been computed for %1-Fold Cross Validation samples.", 
           CVFolds_N)

>>>>

in *this Project* this function is used to clamp the computed movie rating values between 0.5 and 5.
:::

@@

Calculates the average value of the *Mean Squared Errors* calculated with the use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].

::: {.noteblock data-latex=""}
The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
:::

@@

::: { #func.mse_cv.args.r_list .sidebar }
  - **r_list:** A list of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case Study: Recommender Systems / Loss Function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the *Course Textbook (New Edition)*[@IDS2_24-1_LF], computed in the corresponding iteration of *K-fold cross-validation* (the $K$ is $5$ for *this Project*).

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom function [put_log2](#func.put_log2) described above in the [Logging Functions] section of *this Appendix*.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom function [put_log1](#func.put_log1) described above in the [Logging Functions] section of *this Appendix*.
:::
:::

@@

Aggregates the input data frames passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame.

@@

::: { #func.union_cv_results.args.data_list .sidebar }
  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* execution (as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV]).

::: { #func.union_cv_results.details .sidebar }
##### Details
\

This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame for further processing.

::: {.noteblock data-latex=""}
The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
:::

@@

::: {.noteblock data-latex=""}
The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
:::

@@

The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

@@

The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).

::: {.noteblock data-latex=""}
*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).

@@

::: {.noteblock data-latex=""}
The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.

@@

Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

::: { #func.train_user_movie_genre_effect.details .sidebar }
##### Details
\
The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *this Appendix*.

@@

The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).

::: {.noteblock data-latex=""}
*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).

@@

::: {.noteblock data-latex=""}
The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).

::: {.noteblock data-latex=""}
*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
::: {.noteblock data-latex=""}
:::

@@

The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).

@@

::: {.noteblock data-latex=""}
The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

::: {.noteblock data-latex=""}
The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
:::
:::

@@

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function (described below in section [UMGYE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.train_UMGY_effect.cv.usage) subsection of *This Function's Description Section* below.
:::

@@

::: {.noteblock data-latex=""}
The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
:::
:::

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function described below in section [UMGYE Model: Regularization] of *this Appendix*.
:::

@@

The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

Computes the *Day General Effect* (hereafter *DG Effect* or *DGI* for short) (optionally *regularized* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#func.calc_day_general_effect.args.train_set) argument.

@@

This is a helper function that is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).

The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).

::: {.noteblock data-latex=""}
*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

This is a helper function that calculates the *Day General Effect* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the K-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.

::: { #func.calc_day_general_effect.cv.usage .sidebar }
##### Usage
\
```{r eval=FALSE}
```

@@

The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).

@@

::: {.noteblock data-latex=""}
The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

Below is a simplified version of the source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) function:
```{r eval=FALSE}
```
